Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-06 doc/JFLA2022/paper.tex
consistent use of fboxes around snippets
add a remark in Section 2

\section{Changes in the library}
The 2018 article~\cite{JFLA2018paper} presented a formal proof of  a variant of Theorem~\ref{kp:thm2}:

@@

 \begin{itemize}
   \item The game starts at an initial step $i\in\mathbb{N}$ (not necessarily $0$).
   \item  The hydra is always the  representation as a tree of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form. For instance, Fig~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.

@@

 In mathematical terms, if at step $n$ the hydra is associated with the ordinal $\alpha$, at step $n+1$ it is associated with
 $\canonseq{\alpha}{n+1}$, the $(n+1)$th element of the canonical sequence of $\alpha$~\cite{KS81}.

@@

 \begin{figure}[h]
 \inputsnippets{Hprime/HprimeDef}
\caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

Using $H'$s equations as rewrite rules, we can study a realistic example. We take the hydra of figure~\ref{fig:start} and $i=0$ as initial configuration. 
By a sequence of rewritings and inductions, we prove that the number of steps of the considered battle is greater or equal than $2^{2^N}$, where $N=2^{70}-1$.
More generally, we prove that, for $\alpha\geq\omega^\omega$
the function computing the length of the battle starting with the configuration $(\alpha,i)$ is not primitive recursive.

@@

   \begin{figure}[h]
  \centering
  \inputsnippets{Pow/evalPow17LetIn}
  \caption{\label{fig:Pow-evalPow17LetIn}Automatically capturing the output of computations}
\end{figure}

>>>>

\section{Recent developments}
The 2018 article~\cite{JFLA2018paper} presented a formal proof of  a variant of Theorem~\ref{kp:thm2}:

@@

 \begin{itemize}
   \item The game starts at an initial step $i\in\mathbb{N}$ (not necessarily $0$).
   \item  The hydra is always the  representation as a tree of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form (thus, the rightmost branch is also one of the shortest).
     For instance, Fig~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.

@@

 In mathematical terms, if at step $n$ the hydra is associated with the ordinal $\alpha$, at step $n+1$ it is associated with
 $\canonseq{\alpha}{n+1}$, \emph{i.e.} the $(n+1)$th element of the canonical sequence of $\alpha$~\cite{KS81}.

@@

\begin{figure}[h]
  \centering
  \fbox{
    \begin{minipage}[h]{1.0\linewidth}
 \inputsnippets{Hprime/HprimeDef}     
    \end{minipage}}
 \caption{$H'$ definition with the \texttt{coq-equations}
 plug-in~\cite{sozeau:hal-01671777}}
\label{fig:Hprime}
\end{figure}

Using $H'$s equations as rewrite rules, we can study a realistic example. We take the hydra of figure~\ref{fig:start} and $i=0$ as initial configuration. 
By a sequence of rewritings and inductions, we prove that the number of steps of the considered battle is greater or equal than $2^{2^N}$, where $N=2^{70}-1$.
More generally, we prove that, for $\alpha\geq\omega^\omega$, 
the function computing the length of the battle starting with the configuration $(\alpha,i)$ is not primitive recursive.

@@

   \begin{figure}[h]
     \centering
     \fbox{
       \begin{minipage}[h]{1.0\linewidth}
         \inputsnippets{Pow/evalPow17LetIn}
       \end{minipage}}
  \caption{\label{fig:Pow-evalPow17LetIn}Automatically capturing the output of computations}
\end{figure}
